%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{multicol}

\hypersetup{
    pdftoolbar=false,        % show Acrobat’s toolbar?
    pdfmenubar=false,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdfnewwindow=true,      % links in new window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=blue,          % color of internal links (change box color with linkbordercolor)
    filecolor=blue,      % color of file links
    urlcolor=blue           % color of external links
}


\name{Abhishek Nagaraj} % Your name
\address{E62-368 \\ 100 Main Street \\ Cambridge, MA 02142} % Your address
%\address{100 Main Street \\ Cambridge, MA 02139} % Your secondary addess (optional)
\address{(617)~$\cdot$~401~$\cdot$~1662 \\ \texttt{\href{mailto:nagaraj@mit.edu}{nagaraj@mit.edu}}} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf MS/PhD, Massachusetts Institute of Technology} \hfill {\em 2010 -- 2015} \\ 
 Sloan School of Management  \smallskip \\
\emph{Department}: Technological Innovation, Entrepreneurship and Strategic Management (TIES) \\
\emph{Interests}: Innovation and Entrepreneurship of the Digital Economy\\
\emph{Committee}: Scott Stern, Heidi Williams

{\bf MBA, Indian Institute of Management Calcutta} \hfill {\em 2008 -- 2010} \\ 
%%Post Graduate Diploma in Management

{\bf B.S., College of Engineering, Pune} \hfill {\em 2004 -- 2008} \\ 
Computer Science

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Papers}

{\bf Does Copyright Affect Creative Reuse? Evidence from the Google Books Digitization Project} \emph{Working Paper}
\begin{rSubsection}{}{}{}{}
\item Required reading list -- MIT 15.575 ``PhD seminar on Information Technology and Organizations''
\item \textbf{Media Mentions}: \href{http://www.theatlantic.com/technology/archive/2012/07/mit-economist-heres-how-copyright-laws-impoverish-wikipedia/259970/}{The Atlantic}, \href{http://www.jetlaw.org/2012/07/26/copyright-law-and-wikipedia/}{JetLaw}, \href{http://www.techdirt.com/articles/20120719/04103519759/new-research-shows-how-copyright-law-is-keeping-useful-info-off-wikipedia.shtml}{Techdirt}, \href{http://en.wikipedia.org/wiki/Wikipedia:Wikipedia_Signpost/2012-07-30/Recent_research#How_Wikipedia_articles_benefit_from_the_availability_of_public_domain_resources}{Wikipedia Signpost}
\end{rSubsection}

{\bf Do Wiki-pages have parents? An article-level inquiry into Wikipedia's inequalities} \\ \emph{Workshop on Information Technology Systems (WITS) 2009 with P. Seetharaman, R.Roy and A. Dutta}

\end{rSection}

%----------------------------------------------------------------------------------------
%	IN PROGRESS
%----------------------------------------------------------------------------------------

\begin{rSection}{In Progress}

{\bf Does External Knowledge Spur Community Development? Evidence from Digital Mapping} \\ \emph{Job Market Paper}

{\bf Does Open Data Increase Public Transit Ridership?} \\ \emph{with Randall Lewis and Andrew Stuntz}

{\bf Competing with Open : Strategic Lessons from Google Maps} 

{\bf The Impact of Google Books on Readership and Sales : Evidence from the Harvard Libraries}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PRESENTATAIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Invited Presentations}

\begin{rSubsection}{Does External Knowledge Spur Community Development? Evidence from Digital Mapping}{}{}{}
\item Wharton People and Organizations Conference, October 2013
\item MIT XXX
\item NBER XXX
\item NBER XXX
\end{rSubsection}

\begin{rSubsection}{Does Copyright Affect Creative Reuse?}{}{}{}
\item Cyberscholars Working Group, Yale University, January 2014
\item NBER Summer Workshop on Economics of IT and Digitization, July 2013
\item Third Annual Research Roundtable on the Law and Economics of Digital Markets, Searle Center at Northwestern Law School, July 2013
\item Fourth Workshop for Junior Researchers on the Law \& Economics of Intellectual Property and Competition Law, Munich, June 2013
\item Gordon Research Conference on Science \& Technology Policy, August 2012
\item Wikimania International Conference, Washington DC, July 2012 
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	OTHER RESEARCH
%----------------------------------------------------------------------------------------

\begin{rSection}{Other Research Experience}

{\bf Case Writing -- Entrepreneurial Strategy for Leap Motion} \emph{Spring 2013} \\
\emph{Teaching Assistant and case co-author with Prof. Scott Stern for MIT MBA Class 15.911}

{\bf Thomson Reuters Trademark Project} \emph{June - August 2013} \\
\emph{Research Assistant for Prof. Catherine Tucker}

{\bf PubMed Database Parsing} \emph{Jan. 2013, Jan. 2014} \\
\emph{Assisted Profs. Pierre Azoulay and Danielle Li on data collection and parsing for data from PubMed databases. } 

{\bf National Academies of Science Report on Copyright in the Digital Area} \emph{June 2012} \\
\emph{Research Assistant for Prof. Scott Stern}

{\bf Founding Member, MIT/Stanford Mobile Innovation Group} \emph{June 2010 - June 2012} \\
\emph{Research Assistant for Profs. Pai-Ling Yin and Jason Davis. Built large systems to collect and analyze daily-updated database of all apps from Apple, Windows, Blackberry and Android appstores.} 

\end{rSection}

%----------------------------------------------------------------------------------------
%	OTHER RESEARCH
%----------------------------------------------------------------------------------------

\begin{rSection}{Selected Honors}

\begin{rSubsection}{Grants}{}{}{}
\item J. Roberts Beyster Fellowship, 2014
\item Sloan Foundation Research Grant, 2014
\item Center for Digital Business Summer Research Grant, 2014
\item MIT Energy Fellowship, 2012
\item MIT Sloan Doctoral Fellowship, 2010-2015
\end{rSubsection}

\begin{rSubsection}{Awards}{}{}{}
\item Winner, MIT Puzzle Hunt, 2010
\item Top 0.35\% of students out of about 220,000, IIM Common Admission Test (CAT) 2008
\item Winner, IIM Calcutta Great Innovation Challenge 150k Prize, 2010
\item National Semi-Finalist, ESPN Sports Quiz, 2007
\item Silver Medal, National Cyber Olympiad, 2002
\end{rSubsection}

\end{rSection}

%\begin{rSubsection}{Position}{}{}{}
%\end{rSubsection}

\begin{rSection}{Past Positions and Experience}

\begin{rSubsection}{}{}{}{}

\item \textbf{Instructor, Splash} MIT class for high school students, ``Build your own website'', 2010--2013
\item \textbf{Financial Analyst Intern}, Credit Suisse Inc. (Mergers \& Acquisitions), 2009
\item \textbf{Student ``Open Source'' evagelist}, Sun Microsystems India, 2006--2008
\item \textbf{Software Engineer}, IBM Labs Lotus Notes (Intern), 2007
\item \textbf{Co-founder}, Robot Study Circle (RSC) and Jokatimes.com, 2007

\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	OTHER
%----------------------------------------------------------------------------------------
\newpage
\begin{rSection}{INTERESTS AND SKILLS}

{\bf Languages:} English, Hindi, Kannada, Marathi, French (Advanced) \\
{\bf Software:} STATA, R, Matlab, Python, Unix Core, Grid Computing, \LaTeX

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{References}
\begin{multicols}{2}

{\bf Scott Stern}, \\
\emph{NTU Professor of HRM}, \\
David Sarnoff Professor of Management of \\ Technology, MIT Sloan \\
Tel: 617-253-6621 \\ 
\texttt{\href{mailto:sstern@mit.edu}{sstern@mit.edu}} 

{\bf Heidi Williams}, \\
\emph{Assistant Professor} \\
Department of Economics \\
Tel: 617-669-0577 \\
\texttt{\href{mailto:heidiw@mit.edu}{heidiw@mit.edu}}

\columnbreak

{\bf Heidi Williams}, \\
\emph{Assistant Professor} \\
Department of Economics \\
Tel: 617-669-0577 \\
\texttt{\href{mailto:heidiw@mit.edu}{heidiw@mit.edu}}

{\bf Heidi Williams}, \\
\emph{Assistant Professor} \\
Department of Economics \\
Tel: 617-669-0577 \\
\texttt{\href{mailto:heidiw@mit.edu}{heidiw@mit.edu}}


%Scott Stern, \\ School of Management Distinguished Professor\\ MIT Sloan School of Management \\ \href{mailto:sstern@mit.edu}{sstern@mit.edu}

%Scott Stern, \\ School of Management Distinguished Professor\\ MIT Sloan School of Management \\ \href{mailto:sstern@mit.edu}{sstern@mit.edu}


\end{multicols}

\end{rSection}

%----------------------------------------------------------------------------------------
%
\vspace{0.3cm}
\begin{center}
\emph{Last Updated: \today} 
\end{center}

\end{document}
